AggregateCounts

### 2021-07-06 R/AggregateCounts.Rmd

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
library(plotrix)#for std error
library(dplyr)
library(cowplot)
filter <- dplyr::filter
source("~/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/PaSaChronicWounds/R/readTiff.R")
library(EBImage) #for rtiff
```

@@

slicedData<-GetSliceData()

#merge with metadata
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)

metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
sliceDataMeta <- anti_join(sliceDataMeta, remove)

sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
sliceDataMeta<-sliceDataMeta %>% mutate(Height = Zdim*Slice)
sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)

ggplot()+
  geom_point(data = sliceDataMeta,aes(x=NormBiomass,y=Height, color = Condition, shape = TimePoint ),size=2)+

  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  facet_grid(Channel~Condition)+
  theme(plot.title = element_text(hjust = 0.5))

```{r read Tiff functions}

VectorizeTiff<-function(file){
    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
    growth[slice,]<-c(counts, slice, species)
  }

  IterateTiff<-function(fileList, species){
  growth<-matrix(ncol=3, nrow=length(fileList))
  for(slice in 1:(length(fileList))){
    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
    growth[slice,]<-c(counts, slice, species)
  }
  growthDf<-data.fram(growth)
return(growthDf) 
  }

testGetResults<-GetResults()
testGetResults.df<- data.frame(testGetResults)
#this was taken from the PropOc package
SlicesTo3D<-function(filesList,side){
  image1<-readTiff(filesList[1])#read first image to get its dimensions
  image3D <- array(0, c(image1@size[1], image1@size[2], length(filesList)))#preallocate array for image given using image dimensions
  for(i in 1:length(filesList)/3){#keep in mind that it is not zero-index
    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
    image3D[,,i]<-as.array(readImage(fileList[1], convert = TRUE))
  }
  return(image3D)
}

>>>>

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
library(plotrix)#for std error
library(dplyr)
library(cowplot)
filter <- dplyr::filter
library(EBImage) #for rtiff
```

@@

#Input data
#####
#get data from csv file
slicedData<-GetSliceData()
#get metadata
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
#merge files
metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim)
sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
#clean up
remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
sliceDataMeta <- anti_join(sliceDataMeta, remove)

aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "phz_d4_14_Pa" & !SampleCode == "phz_d4_14_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02_Pa" & !SampleCode == "pqsL_d4_02_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04_Pa" & !SampleCode == "pqsL_d4_04_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10_Pa" & !SampleCode == "pqsL_d4_10_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")

#rename variables
sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "wt", "pqsL", "phz"),labels = c('Sa mono','wt co', 'pqsL co', 'phz co'))
sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
#calculate relative biomass
sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)

#####
#Plot Data
#####
ggplot()+
  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
#####
#Filter by Max height of the sample
#####  
sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint) %>% mutate(MaxHeight = max(Height))
ggplot()+
  geom_point(data = maxSlice%>% filter(MaxHeight<120 & MaxHeight>50),aes(x=Replicate,y=MaxHeight, color = Condition),size=4)+
facet_grid(.~TimePoint, scales = "free", space = "free")+
  scale_color_brewer(palette = "Set1")+
  geom_hline(yintercept = 120)+
  geom_hline(yintercept = 50)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),axis.text.x = element_text(angle = 70, hjust = 1))

ggplot()+
  geom_smooth(data = sliceDataMeta %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))

```
```{r Metadata info}
#How many samples have been binarized?
GetTiffNum<-function(sampleName){
  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  sampleFolder<-paste0(parentFolder, sampleName)
  attrList<-str_split(sampleName,"_")[[1]]
  fileList<-list.files(path = sampleFolder, full.names = TRUE)
  tiffSlices<-(length(fileList))/3
  results<-as.data.frame(list(sampleName, attrList[1],attrList[2],attrList[3], tiffSlices))
  colnames(results)<- c("SampleCode","Condition", "TimePoint","Replicate","TiffSlices")
  return(results)
}
tiffNum<-map(metaData.df$SampleCode, GetTiffNum)
tiffNum<-bind_rows(tiffNum)
sortedMetaData<-tiffNum %>% filter(TiffSlices==0)%>% select(SampleCode)
sortedMetaData[order(sortedMetaData),]

tiffStacksNew<-map(metaData.df$SampleCode, GetTiffNum)
tiffStacksNew<-bind_rows(tiffStacksNew)
tiffStacksNew %>% filter(TiffSlices==0) %>% select(SampleCode)
